```{r code=readLines("common.R"), echo=F, message=F, cache=F}
```

## Function start latency

```{r setup-warm, echo=F, cache=T, message=F}
df <- read.csv("start.csv")
cold <- filter(df, backend != "local", start == "cold")
normal <- filter(df, backend != "local", start == "normal")
local <- filter(df, backend == "local")
backend <- unique(normal$backend)

cold.summary <- compute_summary(cold$outer_time, paste(backend, "cold-start latency (s)"))
normal.summary <- compute_summary(normal$outer_time, paste(backend, "Normal-start latency (s)"))
local.summary <- compute_summary(local$outer_time, "local-run latency (s)")

```

### Experiment description
A no-op function was run `r cold.summary$n` times in pairs: first a cold start, then a normal (presumably warm) start.
The total time to execute each run was measured (outer time).

### Summary statistics

```{r echo=F, message=F}
knitr::kable(bind_rows(cold.summary, normal.summary, local.summary), booktabs=T)
```

The mean difference between time to start a warm function and a local function is:
`r round(mean(normal$outer_time - local$outer_time), 3)`s.

Correlation between consecutive pairs of cold/normal start times:
`r report_test(cor.test(local$outer_time, normal$outer_time))`.

The mean difference between time to start a cold function and a warm function is:
`r round(mean(cold$outer_time - normal$outer_time), 3)`s.

Correlation between consecutive pairs of cold/normal start times:
`r report_test(cor.test(cold$outer_time, normal$outer_time))`.


### Distribution


Distribution plots shown in Figures \@ref(fig:cold-start), \@ref(fig:normal-start), and \@ref(fig:local-start).

```{r cold-start, echo=F, cache=T, message=F, warning=F, fig.cap="Distribution of run times of cold-start no-op functions"}
create_distribution_plot(cold$outer_time, cold.summary)
```

```{r normal-start, echo=F, cache=T, message=F, warning=F, fig.cap="Distribution of run times of normal-start no-op functions"}
create_distribution_plot(normal$outer_time, normal.summary)
```

```{r local-start, echo=F, cache=T, message=F, warning=F, fig.cap="Distribution of local run times of normal-start no-op functions"}
create_distribution_plot(local$outer_time, local.summary)
```

