---
title: "SHARP report"
date: "`r Sys.Date()`"
always_allow_html: true
output:
  pdf_book:
    keep_tex: true
    toc: false
---

```{r code=readLines("common.R"), echo=F, message=F, cache=F}
```

```{r setup-000, echo=F, message=F}
require("pander")

knitr::opts_chunk$set(out.width = "75%")

all.summary <- data.frame(Metric = character(),
                          n = integer(),
                          min = numeric(),
                          median = numeric(),
                          mode = numeric(),
                          mean = numeric(),
                          max = numeric(),
                          SE = numeric()
                          )
```

# System description

These experiments were run on the **`r Sys.getenv("REPORTER_BACKEND")`** backend on `r Sys.time()` by user "`r Sys.getenv("REPORTER_USER")`".
The git hash for the current software version was `r Sys.getenv("REPORTER_GIT_HASH")`.

For the hosts running the functions, complete SUT details can be found in the respective .md files attached to this report in the same directory.

For the primary host ("**`r Sys.getenv("REPORTER_HOSTNAME")`**"), the CPU information:

\small
```{r machine-info, echo=F}
cat(readLines('lscpu.out'), sep='\n')
```
\normalsize

----

\newpage

The RAM information was:

\small
```{r memory-info, echo=F}
cat(readLines('memory.out'), sep='\n')
```
\normalsize

---

The GPU information was:

\small
```{r gpu-info, echo=F}
cat(readLines('gpu.out'), sep='\n')
```
\normalsize

---

The R packages used in compiling this report were:

`r pander(sessionInfo())`

\newpage

# Benchmark results

